Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-02-26 tpe_edreview_rebuttal.txt

> 8.  Suggestion: In the line above Eq. (3), if $w >> 0$ then one does
> not need absolute value bars in $|w|<< 1$.
>

Fixed, now reads "consider the proper length from $r=2M$ to
$r=2M(1+w)$ where $w$ is small, $0<w\ll 1$".

> 9.  Question.  2nd line below Eq. (4), why are radial strings
> "arbitrarily" longer than flat space would imply?  It appears the
> difference is a matter of calculation (or measurement), not arbitrary.
> Please explain this choice of words.
>

In mathematical usage (but not in general usage, at least according to
the OED) there is a distinction between "arbitrary" and "arbitrarily".
One usually uses phrases like "arbitrarily large" to convey the idea
that some object may become as large as one desires.

@@

In the manuscript the wording was "radial strings are arbitrarily
longer than flat space would imply", which I think gets the intended
meaning across.

In this case we have the startling result that the discrepancy
approaches infinity ("becomes arbitrarily large") as w approaches
infinity.  I have not seen this result explictly before, yet am
reluctant to claim that it is truly new: after all it is a simple
consequence of a known result (equation 3).  But it is certainly
startling, to me at least.

In any case the original wording was somewhat terse and I have
rephrased.  The manuscript now explicitly states that the discrepancy
in proper length between the Schwarzschild and Euclidean results
approaches infinity as w approaches infinity.

### 2021-02-26 string_physics_educator_revision3.tex
fixes #42

\noindent The discrepancy between the flat-space result of $2Mw$ and
equation~\ref{asymptotic_ell} suggests that, even far from the event
horizon, radial strings are arbitrarily longer than flat space would
imply: a nice illustration of the failure of Euclidean geometry.
Again taking a solar mass black hole but with $w=2\times 10^7$
(corresponding to the orbital radius of Mercury) the difference
between the classical result and equation~\ref{asymptotic_ell} is
about $28\,\mathrm{km}$ of extra string.  However, the prediction is
unlikely to be the basis of a fourth test of general relativity---the
others being Shapiro time delay, bending of starlight, and the
perihelion advance of Mercury~\cite{einstein1916}---as the Sun is not
inside its own Schwarzschild radius.

>>>>

\noindent The discrepancy $\Delta=\ell-2Mw$ between the flat-space result of $2Mw$ and
equation~\ref{asymptotic_ell} has the startling feature that $\lim_{w\longrightarrow\infty}\Delta=\infty$ (because of the $\log w$ term).  This suggests that, even far from the event
horizon, radial strings are arbitrarily longer than flat space would
imply: a nice illustration of the failure of Euclidean geometry.
Again taking a solar mass black hole but with $w=2\times 10^7$
(corresponding to the orbital radius of Mercury) the difference
between the classical result and equation~\ref{asymptotic_ell} is
about $28\,\mathrm{km}$ of extra string.  However, the prediction is
unlikely to be the basis of a fourth test of general relativity---the
others being Shapiro time delay, bending of starlight, and the
perihelion advance of Mercury~\cite{einstein1916}---as the Sun is not
inside its own Schwarzschild radius.
